Total Platform Cyber Protection

### 2016-06-25 paper.tex
make all references lowercase, remove unnecessary tabs in references

Most research into hardware Trojans deal with using side-channel
analysis to identify the malicious Trojan behavior~\cite{Lee2005,
  Agrawal2007, Banga2008, Banga2008a, Jin2008, Du2010, Narasimhan2011,
  Narasimhan2012, Cao2013, Davoodi2013, Dworak2013, Forte2013,
  Liu2013, Liu2014, Bao2015}. This research uses power analysis, heat
analysis, or other side-effects to determine that the hardware is
executing abnormal logic. Unfortunately, this typically requires
building a model based on a ``golden'' or known-good hardware, which
is often not accessible. Furthermore, as chips become more complex,
the Trojan logic become an increasingly smaller portion of the chip,
which in turn reduces the side-channel behavior of the chip
significantly.

Other research has demonstrated the attacks that are possible by
actually implementing Trojan behavior~\cite{King2008, Jin2010,
  Sturton2011, Liu2013, Jin2014, Zhang2014}. This line of research
shows that Trojan logic is feasible for an attack.

Of particular practical interest is a description of \emph{actual
  Trojan logic} discovered in the ProASIC3 Flash FPGA military
chip~\cite{Skorobogatov2012}. While in this case it was not proved
that the logic introduced to the chip was intentionally malicious,
nevertheless there existed functionality in the hardware that was
explicitly denied by the hardware designer.

Another avenue of research is to change the design of the chip itself,
in order to improve the testability of the chip or to increase the
effectiveness of the side-channel analysis~\cite{Chakraborty2008,
  Li2008, Salmani2009, Hicks2010, Rosenfeld2011, Waksman2011,
  Bhunia2013, Davoodi2013, Rajendran2013, Rolt2014}. This line of
research attempts to rethink designing the hardware itself. However, a
major drawback is that this can increase the cost of the hardware and
it must be somehow mandated to be used in COTS components.

JTAG is a main avenue of reverse engineering hardware, so some work
has investigated the problem of securing JTAG access to
hardware~\cite{Rosenfeld2010, Ren2015}. The main idea is to allow only
authenticated users to have access to the JTAG functionality, however
this increases the cost and complexity of implemented JTAG.

Another approach is to change the design of the chip to support
runtime monitoring~\cite{Waksman2010}. In this way, the hardware
itself is monitoring itself, 
% Sai: can we rephrase this^ ? sounds weird %Faris : Removing the first 'itself' may solve the problem.
rather than external analysis of
side-channels. However, this has all the same drawbacks of changing
the design of hardware, in addition to not being robust in the face of
a powerful attacker who is able to alter the design.

Recent approaches suggest to use machine-learning techniques to
identify the Trojan logic~\cite{Haider2015}. Another approach attempts
to use a formal verification technique in order to prove that no
malicious logic was added to the hardware~\cite{Guo2015}.

Finally, there are several surveys conducted on hardware security,
which provide a good overview of the field~\cite{Wang2008,
  Tehranipoor2010, Guin2014, Guin2014a, Guin2014b}.

@@

\subsection{Research}
%Faris: Some fixes below. 
Researchers have attempted to identify real-world attacks on firmware
code~\cite{Tsow2006, Cui2010, Duflot2011, Basnight2013, Cui2013,
  Zaddach2013, Zaddach2013a, Maskiewicz2014, Stuttgen2015}. These
attacks are particularly effective, and researchers have shown that
these are able to persist through a reboot and cannot be detected by
the upper layers.

Other approaches are about how to prevent the tampering of
firmware~\cite{Adelstein2002, Zhou2007, Zhou2009}. These protect from
the threat of tampering or altering the firmware, however it does not
address vulnerable firmware.

Another approach includes runtime monitoring into the
firmware, so that compromises can be detected~\cite{Cui2010a,
  Cui2011}. This approach is further complicated by the lack of
abstractions in the firmware environment.

Recent work has looked into the problem of updating the design of the
firmware so that it has security features, such as memory handling and
avoiding information leakage~\cite{Koeberl2014, Kauer2007}. However,
forcing firmware developers to use such features is an open issue.

Very few work has looked into how to reverse engineer and understand the
firmware~\cite{Zaddach2014}. This problem is of particular interest,
as understanding the semantics of the firmware and how it interacts
with hardware is a key challenge.

Recent work has looked into how to detect vulnerabilities in
firmware~\cite{Davidson2013, Costin2014, Shoshitaishvili2015}. One of
these has an excellent website\footnote{\url{http://firmware.re}}
that contains the results of their reverse engineering and
vulnerability analysis~\cite{Costin2014}.

@@

A major area of research in the Bus and Interconnect layer is work
that shows the dangers of a bus and interconnect that allows malicious
devices to either impersonate devices on the bus or leverage bus
capabilities, particularly in the automotive area~\cite{Bonkoski2013,
  Checkoway2011, Hoppe2008, Koscher2010, Rouf2010, Sang2010}.

The other major area of research is to apply encryption to devices on
the bus and interconnect~\cite{Groza2012, Herrewege2011, Jiang2012,
  Schweppe2011, Stewin2014, Szilagyi2010}. In this way, malicious
devices on the bus cannot impersonate other devices. However, a key
problem with this research direction is how to distribute the keys of
the devices, which is typically done by distributing them in hardware.
Unfortunately, this approach is brittle, as it disallows new devices
from accessing the bus and interconnect.

Other research has investigated how to ensure the integrity of devices
attached to the bus and interconnect using attestation
techniques~\cite{Li2010, Li2011}. These techniques attempt to ensure
that only authorized and unmodified devices are attached to the bus
and interconnect. However, this research has the problem of how to
allow third-party devices to access the bus.

A key problem is how to perform secure updates to devices attached to
the bus and the interconnect~\cite{Larson2008}. This is a challenge
that also has similarities with the firmware layer.

In order to discover malicious communication, researchers have
utilized data flow tracking techniques to discover how the data flows
between devices connect to the bus and interconnect
layers~\cite{Schweppe2012}. Using these techniques, the researchers
are able to identify malicious flows or potential vulnerabilities by
analyzing the way that data flows throughout the system.

Other researchers have explored modeling either the system itself
or the behavior of the devices on the bus~\cite{Stewin2013a,
  Drolia2011}. If the device behavior or the system behavior does not
match the learned model, then an alert is triggered. In this way,
these techniques are similar to anomaly detection techniques, with
similar benefits and drawbacks.

In order to address the issue of devices on the bus able to access
capabilities unauthorized, researchers have tackled the similar
problem of reducing the Trusted Computing Base, essentially reducing
the functionality of the bus and interconnect
layer~\cite{Vasudevan2012, Zhang2013, Zhou2009}. In this way, if the
functionality is not there on the bus, then a malicious device cannot
take advantage of it.

Another approach is to leverage hardware features of the underlying
bus and interconnect system to reduce the impact of an
attack~\cite{Wolf2012, Wojtczuk2011}. However, as these hardware
functionalities must be implemented, it's impact in legacy systems is
limited.

Finally, other research in this area has performed surveys of the
research on this area~\cite{Kleberger2011, Studnia2013, Thom2008,
  Wolf2004, Wolf2007, Wright2011, Zhao2002}.

@@

One area of research is to leverage the vantage point of the
Hypervisor to monitor the guest for security
violations~\cite{Karger1991, Barham2003}, intrusion
detections~\cite{Dunlap2002, Garfinkel2003a, Kourai2005, Chen2008,
  Garfinkel2003b}, checking the integrity of the guest Operating
system~\cite{Seshadri2006, McCune2010}, and identifying rootkits present
in the guest Operating System~\cite{Jones2008, Grace2010}. This work
assumes that the guest can be compromised and that the Hypervisor is
trusted, which, due to vulnerabilities in the Hypervisor, is not
always true.

A significant problem in monitoring or otherwise inspecting a guest
Operating System from the hypervisor layer is the \emph{semantic gap}
problem, where the Hypervisor has no outside knowledge of the
guest-specific Operating System constructs. Therefore, research has
investigated how to overcome this semantic gap~\cite{Jones2006,
  Christodorescu2009, Srinivasan2011}.

Further work in this line has approached the problem of how to monitor
the hypervisor itself by leveraging hardware features~\cite{Azab2010}.

In order to build a secure Hypervisor, the lower layers of the
computing system must also be trusted. Therefore, research into
establishing a Trusted Computing Base, which validates the integrity
of the lower levels for the guest Operating System~\cite{Arbaugh1997,
  Sailer2004, Singaravelu2006} is important for ensuring the security
of the Hypervisor.

One problem of using the Hypervisor as a security primitive is that it
is part of the Trusted Computing Base for the upper layers of the
computing platform. Therefore, attempts have been made to reduce the
trusted base of the Hypervisor itself~\cite{Murray2008, Shinagawa2009,
  Colp2011, Wang2012}.

Other research has looked at creating a secure
Hypervisor~\cite{Robin2000, Belay2012, Szefer2011, Vasudevan2013} with
the possibility of adding functionality to the Hypervisor to support
closed guest Operating Systems~\cite{Garfinkel2003}, offering
applications running in the guest Operating System to hide information
from the guest Operating System~\cite{Chen2008, Yang2008, Jin2011,
  Szefer2012, Azab2011, Zhang2011, Jin2011a, Szefer2011a}, secure
information flow between the guest Operating System drivers and I/O
devices~\cite{Cheng2013}, or designing the hypervisor so that it can
prove that it did not tamper with the guest Operating
System~\cite{Gu2011}.

Another approach to improve the security of the Hypervisor is to
remove the duplicated components from the guest Operating System
layer~\cite{Kivity2014, Madhavapeddy2015}, which effectively reduces
the attack surface of the Operating System layer.

Another interesting approach is to run traditional network middleware
boxes, such as firewalls and Intrusion Detection Systems, as a guest
Operating System of a Hypervisor~\cite{Martins2014}.

Finally, there have been attempts to introduce traditional
application-level security features to Hypervisors, in order to reduce
or prevent vulnerabilities, such as control-flow
integrity~\cite{Wang2010} or manual vulnerability
analysis~\cite{Perez-Botero2013}.

@@

Research into Operating System security has a long and rich history,
which has looked at design flaws in Operating
Systems~\cite{Attanasio1973}. Further research looked at reducing the
permissions of the \emph{root} users, essentially compartmentalizing
the privilege of the Operating System~\cite{Kamp2000, Kurmus2014a}.

Rootkits attempt to persist the attacker's compromise of the operating
system and allow them to hide their malicious behavior from other
applications on the system. Therefore, rootkit detection is an
important research topic in Operating System
security~\cite{Petroni2004, Wang2005, Petroni2007, Payne2008,
  Sharif2009, Yin2010, Bianchi2012}. Another approach is to prevent
the rootkit from altering the Operating System
kernel~\cite{Riley2008a, Wang2009, Grace2010, Gadaleta2011}.

Vulnerability analysis techniques have been used to discover
vulnerabilities in the Operating System kernel before a hacker is able
to use and exploit those vulnerabilities. Static analysis techniques
have been used~\cite{Chou2001, Chen2011}.

Other vulnerability defenses include defenses for specific
vulnerability classes, such as buffer overflows~\cite{Dalton2008}.
Randomization techniques attempt to alter the environment of the
operating system in such a way that the system continues to function
but the attacker's exploit fails~\cite{Lin2009, Giuffrida2012}.
Control-flow integrity techniques have been applied to Operating
System code as well~\cite{Li2011a}.

Other research into Operating System security has looked at how to
protect applications from a malicious or compromised Operating
System~\cite{Ta-min2006, Onarlioglu2013, Li2014}.

% either driver code execute or change `and' to `is'
As driver code executes in kernel space, and is a frequent source of
vulnerabilities~\cite{Kadav2012}, researchers have looked into how to
make drivers more robust~\cite{Ganapathy2008, Hruby2012} or isolated
from the rest of the kernel~\cite{Boyd-Wickizer2010}.

Attack papers show that it is possible to compromise the kernel
without injecting any additional code, using Return Oriented
Programming techniques~\cite{Hund2009}.

A completely different approach is to formally prove the correctness
of the Operating System kernel~\cite{Klein2009}.

Updating Operating Systems with security updates is frequently
difficult, as the Operating System must be restarted. However,
researchers have explored how to apply an update to the Operating
System without rebooting the system~\cite{Arnold2009}.

Some work has been done on removing the operating system
entirely~\cite{Madhavapeddy2010} or trimming/tailoring parts of the
Operating System~\cite{Kurmus2011, Madhavapeddy2013, Howell2013,
  Kurmus2013, Kurmus2014}. This has the security benefit of reducing
the attack surface of the Operating System.

@@

Attempts have been made to measure an application's attack
surface~\cite{Howard2003, Manadhata2007, Manadhata2008, Ruprecht2014}.
This has the benefit of attempting to quantify the attack surface of
an application, which in itself is a difficult problem.

Several research works attempt to reduce the attack surface. Some
approaches try to statically analyze for deadcode, then restrict the
execution of the deadcode during runtime~\cite{Kurmus2011}. Other ways
attempt to leverage compile-time configurability to reduce the attack
surface~\cite{Tartler2012, Kurmus2013, Ruprecht2014}. A different
approach is to reduce the attack surface by partitioning the
application into different privilege levels~\cite{Barth2010, Xu2012}.
Other approaches attempt to restrict the communication between
applications, in order to reduce opportunities for the attacker to
input data to the system~\cite{Kantola2012}.

Finally, other approaches attempt to quantify the attack surface and
measure the actual reduction~\cite{Kurmus2014}.

@@

Modern attackers, exploiting binary applications such as browsers,
media players, or PDF readers, attempt to hijack the control-flow of
the application. If an attacker successfully hijacks the control-flow
of the application, then she has complete control over the execution
of the application. Many vulnerability classes enable control-flow
hijacking, specifically memory corruption vulnerabilities such as
buffer overflows, heap overflows, and format strings~\cite{Szekeres2013}.

@@

Significant progress in this area started with the idea of
control-flow integrity, essentially ensuring dynamically at runtime
that the control-flow of the application does not
deviate~\cite{Abadi2005, Abadi2009}. The first implementations were
deemed infeasible, so later research attempted to improve the
efficiency of control-flow integrity~\cite{Zhang2013, Tice2014,
  Bletsch2011, Zhang2013, Zhang2013a}

Researchers have advanced the state of attacks against control-flow
hijacking. The most advanced of these is return-oriented programming
(ROP), in which an attacker reuses bits of code from the original
application, so that the attacker can hijack the control-flow of the
application without introducing new code~\cite{Roemer2012,
  Bletsch2010, Tran2011}. Researchers have also improved these ROP
techniques~\cite{Checkoway2010, Buchanan2008, Kayaalp2012, Chen2012,
  Goktas2014, Schwartz2011} and applied them to a different
architecture~\cite{Davi2012}.

Other research has looked at defending ROP attacks~\cite{Pappas2012,
  Davi2009, Davi2011, Onarlioglu2010, Gupta2013, Pappas2012, Lu2011,
  Lu2011a, Homescu2012, Gokta2014, Cheng2014, Pappas2013, Snow2013,
  Hiser2012, Wartell2012} or detecting ROP
attacks\cite{Polychronakis2011}. Metastudies have looked at the
effectiveness of these defenses~\cite{Skowyra2013, Schuster2014}.

Finally, other research has shown that even with perfect control-flow
integrity, due to the impreciseness of statically creating the
control-flow graph, an attacker can still hijack the control
flow~\cite{Carlini2015, Schuster2015, Carlini2014, Davi2014}.

@@

Research in logic flaws has typically focused on detecting a certain
type of logic flaw, rather than detecting logic flaws generally. Early
work looked at detecting state violations in web
applications~\cite{Cova2007}.

Other research has looked at preventing access control
vulnerabilities~\cite{dalton09:nemesis}, or statically detecting
them~\cite{Sun2011}.
Some research has looked at other types of logic
flaws, such as
Privilege escalation vulnerabilities~\cite{Monshizadeh2014}, data disclosure
vulnerabilities~\cite{Muthukumaran2015}, single sign-on vulnerabilities~\cite{Zhou2014}, and parameter tampering vulnerabilities~\cite{Bisht2010, Bisht2011}.

Execution After Redirect is another type of logic flaw
vulnerability in web applications~\cite{Doupe2011, Payet2013}.

Work on detecting logic vulnerabilities directly started with
attempting to infer security specifications of an
application~\cite{tan08:autoises, Livshits2009a}. Other approaches dynamically
execute the application to infer likely invariants, then use static
analysis to attempt to find paths that violate those
invariants~\cite{felmetsger10:logic}. Further work tried to find missing
security (authorization) checks automatically, without prior knowledge
of the checks~\cite{Son2011, Son2013}.

% citation needed here for black-box testing
Recent work has looked at detecting logic flaw vulnerabilities in web
applications in a black-box manner---that is, with no knowledge of the
application's source code~\cite{Pellegrino2014}.

@@

Research has been made to automatically generate test inputs for Concolic testing (so that all execution paths can be tested) for major languages like C, C++, and Java~\cite{Garg2013, Jayaraman2009, Sen2005}. Other research in this area includes an approach to combine Random testing~\cite{bird1983automatic} with Concolic execution~\cite{Majumdar2007}, automated Concolic testing for smartphone applications~\cite{anand2012automated}, and using Concolic testing in a distributed, scalable way~\cite{kim2012scalable}. There has also been some work on discussing concolic testing tools and their limitations~\cite{Qu2011}.

There has been significant research in the area of analysis of an application. Dynamic analysis~\cite{ball1999concept} analyzes the code at run time, and much research in this area has been into Taint-based tracking~\cite{Chang2008}, Anomaly Detection~\cite{Cova2007, li11:BLOCK, Li2012}, Context-sensitive sanitization for popular languages and templating languages~\cite{Saxena2011, Samuel2011}, and Binary Analysis~\cite{Song2008}. Other work has looked at automated attack generation using model checking~\cite{martin08:goal_directed_mc}, and classifying the available countermeasures for the C and C++ languages~\cite{Younan2012}.

@@

\subsubsection{Protection against malicious code}
One of the more challenging areas of application security is allowing arbitrary code execution without compromising security. There are situations in which applications need to run user provided code, reuse code that was written in a non-type-safe language, or host another program. For instance, browsers running web applications, or apps being uploaded to app stores. To run code safely and make sure that they are not executing malicious code, there are a number of protection mechanisms that can be used, one of which is Sandboxing, also known as Software Fault Isolation (SFI)~\cite{Wahbe1993}. The idea is to run the code in an isolated environment within the application's address space (called fault domain) and then prevent the code from accessing addresses outside that fault domain.

>>>>

Most research into hardware Trojans deal with using side-channel
analysis to identify the malicious Trojan behavior~\cite{lee2005,
  agrawal2007, banga2008, banga2008a, jin2008, du2010, narasimhan2011,
  narasimhan2012, cao2013, davoodi2013, dworak2013, forte2013,
  liu2013, liu2014, bao2015}. This research uses power analysis, heat
analysis, or other side-effects to determine that the hardware is
executing abnormal logic. Unfortunately, this typically requires
building a model based on a ``golden'' or known-good hardware, which
is often not accessible. Furthermore, as chips become more complex,
the Trojan logic become an increasingly smaller portion of the chip,
which in turn reduces the side-channel behavior of the chip
significantly.

Other research has demonstrated the attacks that are possible by
actually implementing Trojan behavior~\cite{king2008, jin2010,
  sturton2011, liu2013, jin2014, zhang2014}. This line of research
shows that Trojan logic is feasible for an attack.

Of particular practical interest is a description of \emph{actual
  Trojan logic} discovered in the ProASIC3 Flash FPGA military
chip~\cite{skorobogatov2012}. While in this case it was not proved
that the logic introduced to the chip was intentionally malicious,
nevertheless there existed functionality in the hardware that was
explicitly denied by the hardware designer.

Another avenue of research is to change the design of the chip itself,
in order to improve the testability of the chip or to increase the
effectiveness of the side-channel analysis~\cite{chakraborty2008,
  li2008, salmani2009, hicks2010, rosenfeld2011, waksman2011,
  bhunia2013, davoodi2013, rajendran2013, rolt2014}. This line of
research attempts to rethink designing the hardware itself. However, a
major drawback is that this can increase the cost of the hardware and
it must be somehow mandated to be used in COTS components.

JTAG is a main avenue of reverse engineering hardware, so some work
has investigated the problem of securing JTAG access to
hardware~\cite{rosenfeld2010, ren2015}. The main idea is to allow only
authenticated users to have access to the JTAG functionality, however
this increases the cost and complexity of implemented JTAG.

Another approach is to change the design of the chip to support
runtime monitoring~\cite{waksman2010}. In this way, the hardware
is monitoring itself, 
rather than external analysis of
side-channels. However, this has all the same drawbacks of changing
the design of hardware, in addition to not being robust in the face of
a powerful attacker who is able to alter the design.

Recent approaches suggest to use machine-learning techniques to
identify the Trojan logic~\cite{haider2015}. Another approach attempts
to use a formal verification technique in order to prove that no
malicious logic was added to the hardware~\cite{guo2015}.

Finally, there are several surveys conducted on hardware security,
which provide a good overview of the field~\cite{wang2008,
  tehranipoor2010, guin2014, guin2014a, guin2014b}.

@@

\subsection{Research}
%Faris: Some fixes below. 
Researchers have attempted to identify real-world attacks on firmware
code~\cite{tsow2006, cui2010, duflot2011, basnight2013, cui2013,
  zaddach2013, zaddach2013a, maskiewicz2014, stuttgen2015}. These
attacks are particularly effective, and researchers have shown that
these are able to persist through a reboot and cannot be detected by
the upper layers.

Other approaches are about how to prevent the tampering of
firmware~\cite{adelstein2002, zhou2007, zhou2009}. These protect from
the threat of tampering or altering the firmware, however it does not
address vulnerable firmware.

Another approach includes runtime monitoring into the
firmware, so that compromises can be detected~\cite{cui2010a,
  cui2011}. This approach is further complicated by the lack of
abstractions in the firmware environment.

Recent work has looked into the problem of updating the design of the
firmware so that it has security features, such as memory handling and
avoiding information leakage~\cite{koeberl2014, kauer2007}. However,
forcing firmware developers to use such features is an open issue.

Very few work has looked into how to reverse engineer and understand the
firmware~\cite{zaddach2014}. This problem is of particular interest,
as understanding the semantics of the firmware and how it interacts
with hardware is a key challenge.

Recent work has looked into how to detect vulnerabilities in
firmware~\cite{davidson2013, costin2014, shoshitaishvili2015}. One of
these has an excellent website\footnote{\url{http://firmware.re}}
that contains the results of their reverse engineering and
vulnerability analysis~\cite{costin2014}.

@@

A major area of research in the Bus and Interconnect layer is work
that shows the dangers of a bus and interconnect that allows malicious
devices to either impersonate devices on the bus or leverage bus
capabilities, particularly in the automotive area~\cite{bonkoski2013,
  checkoway2011, hoppe2008, koscher2010, rouf2010, sang2010}.

The other major area of research is to apply encryption to devices on
the bus and interconnect~\cite{groza2012, herrewege2011, jiang2012,
  schweppe2011, stewin2014, szilagyi2010}. In this way, malicious
devices on the bus cannot impersonate other devices. However, a key
problem with this research direction is how to distribute the keys of
the devices, which is typically done by distributing them in hardware.
Unfortunately, this approach is brittle, as it disallows new devices
from accessing the bus and interconnect.

Other research has investigated how to ensure the integrity of devices
attached to the bus and interconnect using attestation
techniques~\cite{li2010, li2011}. These techniques attempt to ensure
that only authorized and unmodified devices are attached to the bus
and interconnect. However, this research has the problem of how to
allow third-party devices to access the bus.

A key problem is how to perform secure updates to devices attached to
the bus and the interconnect~\cite{larson2008}. This is a challenge
that also has similarities with the firmware layer.

In order to discover malicious communication, researchers have
utilized data flow tracking techniques to discover how the data flows
between devices connect to the bus and interconnect
layers~\cite{schweppe2012}. Using these techniques, the researchers
are able to identify malicious flows or potential vulnerabilities by
analyzing the way that data flows throughout the system.

Other researchers have explored modeling either the system itself
or the behavior of the devices on the bus~\cite{stewin2013a,
  drolia2011}. If the device behavior or the system behavior does not
match the learned model, then an alert is triggered. In this way,
these techniques are similar to anomaly detection techniques, with
similar benefits and drawbacks.

In order to address the issue of devices on the bus able to access
capabilities unauthorized, researchers have tackled the similar
problem of reducing the Trusted Computing Base, essentially reducing
the functionality of the bus and interconnect
layer~\cite{vasudevan2012, zhang2013, zhou2009}. In this way, if the
functionality is not there on the bus, then a malicious device cannot
take advantage of it.

Another approach is to leverage hardware features of the underlying
bus and interconnect system to reduce the impact of an
attack~\cite{wolf2012, wojtczuk2011}. However, as these hardware
functionalities must be implemented, it's impact in legacy systems is
limited.

Finally, other research in this area has performed surveys of the
research on this area~\cite{kleberger2011, studnia2013, thom2008,
  wolf2004, wolf2007, wright2011, zhao2002}.

@@

One area of research is to leverage the vantage point of the
Hypervisor to monitor the guest for security
violations~\cite{karger1991, barham2003}, intrusion
detections~\cite{dunlap2002, garfinkel2003a, kourai2005, chen2008,
  garfinkel2003b}, checking the integrity of the guest Operating
system~\cite{seshadri2006, mccune2010}, and identifying rootkits present
in the guest Operating System~\cite{jones2008, grace2010}. This work
assumes that the guest can be compromised and that the Hypervisor is
trusted, which, due to vulnerabilities in the Hypervisor, is not
always true.

A significant problem in monitoring or otherwise inspecting a guest
Operating System from the hypervisor layer is the \emph{semantic gap}
problem, where the Hypervisor has no outside knowledge of the
guest-specific Operating System constructs. Therefore, research has
investigated how to overcome this semantic gap~\cite{jones2006,
  christodorescu2009, srinivasan2011}.

Further work in this line has approached the problem of how to monitor
the hypervisor itself by leveraging hardware features~\cite{azab2010}.

In order to build a secure Hypervisor, the lower layers of the
computing system must also be trusted. Therefore, research into
establishing a Trusted Computing Base, which validates the integrity
of the lower levels for the guest Operating System~\cite{arbaugh1997,
  sailer2004, singaravelu2006} is important for ensuring the security
of the Hypervisor.

One problem of using the Hypervisor as a security primitive is that it
is part of the Trusted Computing Base for the upper layers of the
computing platform. Therefore, attempts have been made to reduce the
trusted base of the Hypervisor itself~\cite{murray2008, shinagawa2009,
  colp2011, wang2012}.

Other research has looked at creating a secure
Hypervisor~\cite{robin2000, belay2012, szefer2011, vasudevan2013} with
the possibility of adding functionality to the Hypervisor to support
closed guest Operating Systems~\cite{garfinkel2003}, offering
applications running in the guest Operating System to hide information
from the guest Operating System~\cite{chen2008, yang2008, jin2011,
  szefer2012, azab2011, zhang2011, jin2011a, szefer2011a}, secure
information flow between the guest Operating System drivers and I/O
devices~\cite{cheng2013}, or designing the hypervisor so that it can
prove that it did not tamper with the guest Operating
System~\cite{gu2011}.

Another approach to improve the security of the Hypervisor is to
remove the duplicated components from the guest Operating System
layer~\cite{kivity2014, madhavapeddy2015}, which effectively reduces
the attack surface of the Operating System layer.

Another interesting approach is to run traditional network middleware
boxes, such as firewalls and Intrusion Detection Systems, as a guest
Operating System of a Hypervisor~\cite{martins2014}.

Finally, there have been attempts to introduce traditional
application-level security features to Hypervisors, in order to reduce
or prevent vulnerabilities, such as control-flow
integrity~\cite{wang2010} or manual vulnerability
analysis~\cite{Perez-Botero2013}.

@@

Research into Operating System security has a long and rich history,
which has looked at design flaws in Operating
Systems~\cite{attanasio1973}. Further research looked at reducing the
permissions of the \emph{root} users, essentially compartmentalizing
the privilege of the Operating System~\cite{kamp2000, kurmus2014a}.

Rootkits attempt to persist the attacker's compromise of the operating
system and allow them to hide their malicious behavior from other
applications on the system. Therefore, rootkit detection is an
important research topic in Operating System
security~\cite{petroni2004, wang2005, petroni2007, payne2008,
  sharif2009, yin2010, bianchi2012}. Another approach is to prevent
the rootkit from altering the Operating System
kernel~\cite{riley2008, wang2009, grace2010, gadaleta2011}.

Vulnerability analysis techniques have been used to discover
vulnerabilities in the Operating System kernel before a hacker is able
to use and exploit those vulnerabilities. Static analysis techniques
have been used~\cite{chou2001, chen2011}.

Other vulnerability defenses include defenses for specific
vulnerability classes, such as buffer overflows~\cite{dalton2008}.
Randomization techniques attempt to alter the environment of the
operating system in such a way that the system continues to function
but the attacker's exploit fails~\cite{lin2009, giuffrida2012}.
Control-flow integrity techniques have been applied to Operating
System code as well~\cite{li2011a}.

Other research into Operating System security has looked at how to
protect applications from a malicious or compromised Operating
System~\cite{ta-min2006, onarlioglu2013, li2014}.

% either driver code execute or change `and' to `is'
As driver code executes in kernel space, and is a frequent source of
vulnerabilities~\cite{kadav2012}, researchers have looked into how to
make drivers more robust~\cite{ganapathy2008, hruby2012} or isolated
from the rest of the kernel~\cite{boyd-wickizer2010}.

Attack papers show that it is possible to compromise the kernel
without injecting any additional code, using Return Oriented
Programming techniques~\cite{hund2009}.

A completely different approach is to formally prove the correctness
of the Operating System kernel~\cite{klein2009}.

Updating Operating Systems with security updates is frequently
difficult, as the Operating System must be restarted. However,
researchers have explored how to apply an update to the Operating
System without rebooting the system~\cite{arnold2009}.

Some work has been done on removing the operating system
entirely~\cite{madhavapeddy2010} or trimming/tailoring parts of the
Operating System~\cite{kurmus2011, madhavapeddy2013, howell2013,
  kurmus2013, kurmus2014}. This has the security benefit of reducing
the attack surface of the Operating System.

@@

Attempts have been made to measure an application's attack
surface~\cite{howard2003, manadhata2007, manadhata2008, ruprecht2014}.
This has the benefit of attempting to quantify the attack surface of
an application, which in itself is a difficult problem.

Several research works attempt to reduce the attack surface. Some
approaches try to statically analyze for deadcode, then restrict the
execution of the deadcode during runtime~\cite{kurmus2011}. Other ways
attempt to leverage compile-time configurability to reduce the attack
surface~\cite{tartler2012, kurmus2013, ruprecht2014}. A different
approach is to reduce the attack surface by partitioning the
application into different privilege levels~\cite{barth2010, xu2012}.
Other approaches attempt to restrict the communication between
applications, in order to reduce opportunities for the attacker to
input data to the system~\cite{kantola2012}.

Finally, other approaches attempt to quantify the attack surface and
measure the actual reduction~\cite{kurmus2014}.

@@

Modern attackers, exploiting binary applications such as browsers,
media players, or PDF readers, attempt to hijack the control-flow of
the application. If an attacker successfully hijacks the control-flow
of the application, then she has complete control over the execution
of the application. Many vulnerability classes enable control-flow
hijacking, specifically memory corruption vulnerabilities such as
buffer overflows, heap overflows, and format strings~\cite{szekeres2013}.

@@

Significant progress in this area started with the idea of
control-flow integrity, essentially ensuring dynamically at runtime
that the control-flow of the application does not
deviate~\cite{abadi2005, abadi2009}. The first implementations were
deemed infeasible, so later research attempted to improve the
efficiency of control-flow integrity~\cite{zhang2013, tice2014,
  bletsch2011, zhang2013, zhang2013a}.

Researchers have advanced the state of attacks against control-flow
hijacking. The most advanced of these is return-oriented programming
(ROP), in which an attacker reuses bits of code from the original
application, so that the attacker can hijack the control-flow of the
application without introducing new code~\cite{roemer2012,
  bletsch2010, tran2011}. Researchers have also improved these ROP
techniques~\cite{checkoway2010, buchanan2008, kayaalp2012, chen2012,
  goktas2014, schwartz2011} and applied them to a different
architecture~\cite{davi2012}.

Other research has looked at defending ROP attacks~\cite{pappas2012,
  davi2009, davi2011, onarlioglu2010, gupta2013, pappas2012, lu2011,
  lu2011a, homescu2012, gokta2014, cheng2014, pappas2013, snow2013,
  hiser2012, wartell2012} or detecting ROP
attacks\cite{polychronakis2011}. Metastudies have looked at the
effectiveness of these defenses~\cite{skowyra2013, schuster2014}.

Finally, other research has shown that even with perfect control-flow
integrity, due to the impreciseness of statically creating the
control-flow graph, an attacker can still hijack the control
flow~\cite{carlini2015, schuster2015, carlini2014, davi2014}.

@@

Research in logic flaws has typically focused on detecting a certain
type of logic flaw, rather than detecting logic flaws generally. Early
work looked at detecting state violations in web
applications~\cite{cova2007}.

Other research has looked at preventing access control
vulnerabilities~\cite{dalton09:nemesis}, or statically detecting
them~\cite{sun2011}.
Some research has looked at other types of logic
flaws, such as
Privilege escalation vulnerabilities~\cite{monshizadeh2014}, data disclosure
vulnerabilities~\cite{muthukumaran2015}, single sign-on vulnerabilities~\cite{zhou2014}, and parameter tampering vulnerabilities~\cite{bisht2010, bisht2011}.

Execution After Redirect is another type of logic flaw
vulnerability in web applications~\cite{doupe2011, payet2013}.

Work on detecting logic vulnerabilities directly started with
attempting to infer security specifications of an
application~\cite{tan08:autoises, Livshits2009a}. Other approaches dynamically
execute the application to infer likely invariants, then use static
analysis to attempt to find paths that violate those
invariants~\cite{felmetsger10:logic}. Further work tried to find missing
security (authorization) checks automatically, without prior knowledge
of the checks~\cite{son2011, son2013}.

% citation needed here for black-box testing
Recent work has looked at detecting logic flaw vulnerabilities in web
applications in a black-box manner---that is, with no knowledge of the
application's source code~\cite{pellegrino2014}.

@@

Research has been made to automatically generate test inputs for Concolic testing (so that all execution paths can be tested) for major languages like C, C++, and Java~\cite{garg2013, jayaraman2009, sen2005}. Other research in this area includes an approach to combine Random testing~\cite{bird1983automatic} with Concolic execution~\cite{majumdar2007}, automated Concolic testing for smartphone applications~\cite{anand2012automated}, and using Concolic testing in a distributed, scalable way~\cite{kim2012scalable}. There has also been some work on discussing concolic testing tools and their limitations~\cite{qu2011}.

There has been significant research in the area of analysis of an application. Dynamic analysis~\cite{ball1999concept} analyzes the code at run time, and much research in this area has been into Taint-based tracking~\cite{chang2008}, Anomaly Detection~\cite{cova2007, li11:block, li2012}, Context-sensitive sanitization for popular languages and templating languages~\cite{saxena2011, samuel2011}, Binary Analysis~\cite{song2008}, and Logic vulnerabilities~\cite{felmetsger2010}. Other work has looked at automated attack generation using model checking~\cite{martin08:goal_directed_mc}, and classifying the available countermeasures for the C and C++ languages~\cite{younan2012}.

@@

\subsubsection{Protection against malicious code}
One of the more challenging areas of application security is allowing arbitrary code execution without compromising security. There are situations in which applications need to run user provided code, reuse code that was written in a non-type-safe language, or host another program. For instance, browsers running web applications, or apps being uploaded to app stores. To run code safely and make sure that they are not executing malicious code, there are a number of protection mechanisms that can be used, one of which is Sandboxing, also known as Software Fault Isolation (SFI)~\cite{wahbe1993}. The idea is to run the code in an isolated environment within the application's address space (called fault domain) and then prevent the code from accessing addresses outside that fault domain.
